### 2023-05-26 paper.tex
new commit

\documentclass[english]{cenarticle}
%----------------------------------------------------------------------------------------
%	PUBLISH INFO (not for authors)
%----------------------------------------------------------------------------------------
%
\issn{2179-460X}
%
\volume{44}
%
\eJournal{eXX}
%
\doi{https://doi.org/10.5902/2179460Xxxxxx}
%
\submitionDate{xx/xx/xx}
%
\approvalDate{xx/xx/xx}
%
\publishDate{xx/xx/xx}
%
\yearonfooter{xxxx}
%
%----------------------------------------------------------------------------------------
%	YOUR PACKAGES
%----------------------------------------------------------------------------------------
%
\usepackage{pgfplots}
\usepackage{caption}
\usepackage{graphicx}

@@

\usepackage{booktabs}
\usepackage{multirow}
%
%----------------------------------------------------------------------------------------
%	YOUR CONFIGURATIONS
%----------------------------------------------------------------------------------------
%
\captionsetup{%
  font=footnotesize,
  labelfont=bf,
  singlelinecheck=false,
  tableposition=top,
  labelsep=endash,
  justification=raggedright,
  margin={0pt,0pt}
}

\sisetup{math-micro=\text{µ},text-micro=µ}
%
%----------------------------------------------------------------------------------------
%	YOUR NEW COMMANDS
%----------------------------------------------------------------------------------------
%
\renewcommand{\thefigure}{\arabic{figure}}
%----------------------------------------------------------------------------------------
%	PAPER INFO (for authors)
%----------------------------------------------------------------------------------------
%
\cenSection{Chemistry}
%
\englishTitle{Interference of Lightning and Thunder on Radioactivity: A Novel Approach in the air}
%
\portugueseTitle{Interferência de Raios e Trovões na Radioatividade: Uma Nova Abordagem no Ar}
%
\author{
  %\authorinfo[ORCID]{NAME}{AFFILIATION},
  \authorinfo[0000-0000-0000-0000]{Charles Babbage}{I},
  \authorinfo[]{Ada Lovelace}{II},
  \authorinfo[0000-0000-0000-0000]{Pierre Curie}{I},
  \authorinfo[0000-0000-0000-0000]{Marie Curie}{},
  \authorinfo[0000-0000-0000-0000]{Grace Hopper}{II},
  \authorinfo[0000-0000-0000-0000]{Santos Dumont}{},
  \authorinfo[]{Nikola Tesla}{},
  \authorinfo[0000-0000-0000-0000]{Galileu Galilei}{I},
  \authorinfo[0000-0000-0000-0000]{Charles Darwin}{I},
  \authorinfo[0000-0000-0000-0000]{Barbara McClintock}{}
}
%
\affil{ 
  \affiliation{I}{Brown University, USA}
  \affiliation{II}{University of Oxford, UK}
}

@@

\englishKeywords{lightning, radioactivity, airborne experiment, storm}

@@

\begin{figure}[!h]
  \newcommand\x{0.25}
  \caption{The 4th generation of the Electroplumbus Nimbodetector}
  \begin{center}
    \vspace{-3mm}
		\begin{minipage}[t]{\x\linewidth}
			\includegraphics[width = \textwidth, trim={0 0.8cm 0 0.9cm},clip]{images/nimbodetector.png}	
      \captionsetup{justification=centering, font=footnotesize}
			\caption*{(a)}\label{fig:triangle2a}
		\end{minipage}
		\begin{minipage}[t]{\x\linewidth}
			\includegraphics[width = \textwidth, trim={0 0.8cm 0 0.9cm},clip]{images/sensor.png}	
      \captionsetup{justification=centering, font=footnotesize}
			\caption*{(b)}\label{fig:triangle2b}
		\end{minipage}\\
  \end{center}%
  \vspace{-1mm}
  {\footnotesize
  Source: Craiyon website, see \citep{Craiyon}.\\
  Caption: The (a) figure displays the core of the device with the Plumbus Combobulator inside and (b) shows the lightning detector filled by enriched Glowing Schleem substance.\\
  }
	\label{fig:triangle2}
  \end{figure}\vspace{-9mm}
%
\subsection{Data Collection}

@@

At the core of the data storage mechanism is the utilization of punched paper, designed to withstand various environmental conditions. This robust material ensures the durability and integrity of the captured lightning data, even during adverse weather conditions such as rainfall. The waterproof nature of the paper safeguards the data from moisture, allowing for uninterrupted data collection.

The adapted Plumbus Combobulator employs a $\SI{0.47}{\micro\meter}$ needle, precisely marking the punched paper as the lightning data is processed. This needle-based mechanism creates a distinct pattern that represents the collected information. With each stroke, a tangible record of the lightning data is imprinted onto the punched paper.

The paper-based storage medium enables efficient and reliable data preservation. Each $\SI{100}{\milli\meter}$ segment of the punched paper corresponds to a substantial $\SI{1.2E6}{\byte}$ of information. This capacity ensures ample storage space for capturing an extensive volume of lightning data during experiments.

@@

\subsection{The Branzine}

According to Plumbus Combobulator manufacturer \citep{PlumbusManual}, the Branzine levels can cause Electroplumbus Nimbodetector malfunctions. Because that a preliminary exploratory flight was undertaken to examine the influence of altitude on Branzine levels, considering both air samples collected with and without rainfall.

During the flight, air samples were gathered at various altitudes to measure the concentration of Branzine, by using the Branzine detector\footnote{Digital Bz897U, available on $^{\circledR}$Airbone Laboratory Instrument Inc.}. The samples were divided into two groups: those collected during rainfall and those obtained under dry conditions. This differentiation aimed to explore any potential impact of precipitation on Branzine levels.

The collected data was send to the laboratory, and the results are summarized in the table below:

\begin{table}[!h]
\caption{Branzine levels}
\vspace{-6mm}
\footnotesize
\begin{center}
  \begin{tabular}{@{}lccc@{}}
  \toprule
                                         & altitude & \multicolumn{2}{c}{Branzine levels {$[ppm]$}} \\ \cmidrule(l){3-4} 
                                         & {$[m]$}  & on rain             & lack of rain            \\ \midrule
  \multirow{8}{*}{\rotatebox[origin=c]{90}{under the clouds} } 
                                         & $100 \pm 1$      & $0.005 \pm 0.001$   &     $0.006 \pm 0.001$  \\
                                         & $200 \pm 1$      & $1.265 \pm 0.001$   &     $1.260 \pm 0.001$  \\
                                         & $500 \pm 1$      & $40.1  \pm 0.01$    &      $40.2 \pm 0.01$   \\
                                         & $1000\pm 1$      & $392   \pm 5$       &      $395  \pm 5$      \\
                                         & $2000\pm 1$      & $609   \pm 5$       &      $607  \pm 5$      \\
                                         & $3000\pm 1$      & $2709  \pm 10$      &     $2701  \pm 10$     \\
                                         & $4000\pm 1$      & $12701 \pm 10$      &     $12699 \pm 10$     \\
                                         & $5000\pm 1$      & $100831 \pm 10$     &     $100827 \pm 10$    \\ \midrule
  \multirow{7}{*}{\rotatebox[origin=c]{90}{above the clouds} }
                                         & $6000\pm 1$       & $-$                &    $280190 \pm 10$                 \\
                                         & $6200\pm 1$       & $-$                &    $518914 \pm 100$                \\ 
                                         & $6400\pm 1$       & $-$                &    $819827 \pm 100$                \\ 
                                         & $6600\pm 1$       & $-$                &    $100827 \pm 100$                \\ 
                                         & $6800\pm 1$       & $-$                &    $1124225 \pm 1000$              \\ 
                                         & $7000\pm 1$       & $-$                &    $6131823 \pm 1000$              \\ 
                                         & $8000\pm 1$       & $-$                &    $9792921 \pm 1000$              \\ \bottomrule
  \end{tabular}\\[3mm]
\end{center}
Caption: The Branzine levels in relation to altitude, over the Atlantic Ocean (August, 1987).\\
\end{table}

Upon analyzing the data, it was observed that there is a increase in Branzine levels with increasing altitude. However, the rise remained below $0.2\%$, indicating an insignificant effect on the Plumbus performance. These findings align with prior research \citep{Gagaia1923}, which suggests that Branzine levels typically exhibit a notable increase of over $5\%$ in specific regions such as winter sections or the Bermuda Triangle ($32\%$).
\vfill

@@

>>>>

% meia risca meio traço alt+0150
% heat transfer rate through radiation
% o core tem termometro do veículo que é separado. A luz aquece o sheeem (baixa capacidade termica) e é determinada a temperatura

\documentclass[portuguese]{cenarticle}
%----------------------------------------------------------------------------------------
%	PUBLISH INFO (not for authors)
%----------------------------------------------------------------------------------------
%
\issn{2179-460X}
%
\volume{44}
%
\eJournal{eXX}
%
\doi{https://doi.org/10.5902/2179460Xxxxxx}
%
\submitionDate{xx/xx/xx}
%
\approvalDate{xx/xx/xx}
%
\publishDate{xx/xx/xx}
%
\yearonfooter{xxxx}
%
%----------------------------------------------------------------------------------------
%	YOUR PACKAGES
%----------------------------------------------------------------------------------------
%
\usepackage{pgfplots}
\usepackage{graphicx}

@@

\usepackage{booktabs}
\usepackage{multirow}
%
%----------------------------------------------------------------------------------------
%	YOUR CONFIGURATIONS
%----------------------------------------------------------------------------------------
%
\sisetup{math-micro=\text{µ},text-micro=µ}
%
%----------------------------------------------------------------------------------------
%	YOUR NEW COMMANDS
%----------------------------------------------------------------------------------------
%
\renewcommand{\thefigure}{\arabic{figure}}
%----------------------------------------------------------------------------------------
%	PAPER INFO (for authors)
%----------------------------------------------------------------------------------------
%
\cenSection{Chemistry}
%
\englishTitle{Interference of Lightning and Thunder on Radioactivity: A Novel Approach in the air}
%
\portugueseTitle{Interferência de Raios e Trovões na Radioatividade: Uma Nova Abordagem no Ar}
%
\author{
  %\authorinfo[ORCID]{NAME}{AFFILIATION},
  \authorinfo[0000-0000-0000-0000]{Charles Babbage}{I},
  \authorinfo[]{Ada Lovelace}{II},
  \authorinfo[0000-0000-0000-0000]{Pierre Curie}{I},
  \authorinfo[0000-0000-0000-0000]{Marie Curie}{},
  \authorinfo[0000-0000-0000-0000]{Grace Hopper}{II},
  \authorinfo[0000-0000-0000-0000]{Santos Dumont}{},
  \authorinfo[]{Nikola Tesla}{},
  \authorinfo[0000-0000-0000-0000]{Galileu Galilei}{I},
  \authorinfo[0000-0000-0000-0000]{Charles Darwin}{I},
  \authorinfo[0000-0000-0000-0000]{Barbara McClintock}{}
}
%
\affil{ 
  \affiliation{I}{Brown University, USA}
  \affiliation{II}{University of Oxford, UK}
}

@@

\englishKeywords{Lightning; Radioactivity; Airborne experiment; Storm}

@@

\begin{figure}[!h]
  \newcommand\x{0.25}
  \caption{The 4th generation of the Electroplumbus Nimbodetector}
  \begin{center}
    \vspace{-3mm}
		\begin{minipage}[t]{\x\linewidth}
			\includegraphics[width = \textwidth, trim={0 0.8cm 0 0.9cm},clip]{images/nimbodetector.png}	
      \captionsetup{justification=centering, font=footnotesize}
			\caption*{(a)}\label{fig:triangle2a}
		\end{minipage}
		\begin{minipage}[t]{\x\linewidth}
			\includegraphics[width = \textwidth, trim={0 0.8cm 0 0.9cm},clip]{images/sensor.png}	
      \captionsetup{justification=centering, font=footnotesize}
			\caption*{(b)}\label{fig:triangle2b}
		\end{minipage}\\
  \end{center}%
  \vspace{-1mm}
  {\footnotesize
  Source: Craiyon website, see \citep{Craiyon}\\
  Caption: The (a) figure displays the core of the device with the Plumbus Combobulator inside and (b) shows the lightning detector filled by enriched Glowing Schleem substance\\
  }
	\label{fig:triangle2}
  \end{figure}\vspace{-9mm}
%
\subsection{Data Collection}

@@

At the core of the data storage mechanism is the utilization of punched tape, designed to withstand various environmental conditions. This robust material ensures the durability and integrity of the captured lightning data, even during adverse weather conditions such as rainfall. The waterproof nature of the tape safeguards the data from moisture, allowing for uninterrupted data collection.

The adapted Plumbus Combobulator employs a $\SI{0.47}{\micro\meter}$ needle, precisely marking the punched tape as the lightning data is processed. This needle-based mechanism creates a distinct pattern that represents the collected information. With each stroke, a tangible record of the lightning data is imprinted onto the punched tape.

The tape-based storage medium enables efficient and reliable data preservation. Each $\SI{100}{\milli\meter}$ segment of the punched tape corresponds to a substantial $\SI{1.2E6}{\byte}$ of information. This capacity ensures ample storage space for capturing an extensive volume of lightning data during experiments.

@@

\subsection{The Branzine levels}

According to the Plumbus Combobulator manufacturer's manual \citep{PlumbusManual}, high levels of Branzine can potentially lead to malfunctions in the Electroplumbus Nimbodetector. Therefore, a preliminary exploratory flight was conducted to investigate the relationship between altitude and Branzine levels. 
During the flight, air samples were gathered at various altitudes to measure the concentration of Branzine, by using the Branzine detector\footnote{Digital Bz897U, available on $^{\circledR}$Airbone Laboratory Instrument Inc.}. The samples were divided into two groups: those collected during rainfall and those obtained under dry conditions. This differentiation aimed to explore any potential impact of precipitation on Branzine levels.

The  data was sent to the laboratory, and the results are bellow summarized:

\begin{table}[!h]
\caption{Branzine levels}
\vspace{-5mm}
\footnotesize
\begin{center}
  \begin{tabular}{@{}lccc@{}}
  \toprule
                                         & altitude & \multicolumn{2}{c}{Branzine levels {$[ppm]$}} \\ \cmidrule(l){3-4} 
                                         & {$[m]$}  & on rain             & lack of rain            \\ \midrule
  \multirow{8}{*}{\rotatebox[origin=c]{90}{under the clouds} } 
                                         & $100 \pm 1$      & $0.005 \pm 0.001$   &     $0.006 \pm 0.001$  \\
                                         & $200 \pm 1$      & $1.265 \pm 0.001$   &     $1.260 \pm 0.001$  \\
                                         & $500 \pm 1$      & $40.1  \pm 0.1$    &      $40.2 \pm 0.1$   \\
                                         & $1000\pm 1$      & $392   \pm 5$       &      $395  \pm 5$      \\
                                         & $2000\pm 1$      & $609   \pm 5$       &      $607  \pm 5$      \\
                                         & $3000\pm 1$      & $2709  \pm 10$      &     $2701  \pm 10$     \\
                                         & $4000\pm 1$      & $12701 \pm 10$      &     $12699 \pm 10$     \\
                                         & $5000\pm 1$      & $100831 \pm 10$     &     $100827 \pm 10$    \\ \midrule
  \multirow{7}{*}{\rotatebox[origin=c]{90}{above the clouds} }
                                         & $6000\pm 1$       & $-$                &    $280190 \pm 10$                 \\
                                         & $6200\pm 1$       & $-$                &    $518914 \pm 100$                \\ 
                                         & $6400\pm 1$       & $-$                &    $819827 \pm 100$                \\ 
                                         & $6600\pm 1$       & $-$                &    $100827 \pm 100$                \\ 
                                         & $6800\pm 1$       & $-$                &    $1124225 \pm 1000$              \\ 
                                         & $7000\pm 1$       & $-$                &    $6131823 \pm 1000$              \\ 
                                         & $8000\pm 1$       & $-$                &    $9792921 \pm 1000$              \\ \bottomrule
  \end{tabular}\\[3mm]
\end{center}
Caption: The Branzine levels in relation to altitude, over the Atlantic Ocean (August, 1987).\\
\end{table}
\vspace{-6mm}
Upon analyzing the data, it was observed that there is a increase in Branzine levels with increasing altitude. However, the rise remained below $0.2\%$, indicating an insignificant effect on the Plumbus performance. These findings align with prior research \citep{Gagaia1923}, which suggests that Branzine levels typically exhibit a notable increase of over $5\%$ in some conditions such as winter seasons or above the Bermuda's Triangle ($32\%$).

\subsection{The radiation levels}

Despite the influence of Branzine on the detector, it has been determined that the Electroplumbus Nimbodetector is safe to use under the tested conditions. The Electroplumbus Nimbodetector was successfully installed on the 14-bis flying vehicle, and a series of tests were conducted at altitudes ranging from $\SI{100}{\meter}$ to $\SI{6000}{\meter}$.

The evaluation began by examining the performance of the Nimbus Detector under heavy rain conditions, comparing the recorded data to measurements obtained in a rainless environment above the clouds. A total of $\SI{12}{\meter}$ of data were collected and recorded on punched tape, with $\SI{30}{\centi\meter}$ obtained in the absence of rain and the remaining length obtained during rainfall.

After the evaluation, the collected data in the form of punched tape was sent for analysis. The punched tape contained the recorded information obtained by the Nimbus Detector during the data collection. To process and analyze the data, the Monrobot XI computer was used, employing the Foobar Algorithm programmed in FORTRAN.

\begin{equation}\label{StefanBoltzmannLaw}
  j^{\star}=\sigma\varepsilon T^{4}
\end{equation}
%
\noindent where,
%
\begin{equation}\label{StefanBoltzmannConstant }
  \sigma=5.6704\times10^{-8} Wm^{-2}K^{-4}
\end{equation}

\begin{equation}
  j^{\star}=\sigma\varepsilon T^{4}
\end{equation}

\begin{equation}\label{StefanBoltzmannLaw}
  \begin{split}
    \frac{P}{A}&=j^{\star}=\sigma\varepsilon (T_{v}^{4} - T_{a}^{4}) \\
  \end{split}
\end{equation}

\noindent where,

\begin{equation}\label{StefanBoltzmannLaw}
  \begin{split}
    P = \frac{Q}{t}
  \end{split}
\end{equation}

@@

The chart presents the number of lightning strikes detected by the Nimbus Detector within different altitude ranges. As altitude increased, the number of recorded lightning strikes also exhibited an upward trend.
